The Gravettian-Solutrean transition in westernmost Iberia: new data from the sites of Vale Boi and Lapa do Picareiro

### 2020-04-22 analysis/paper/paper.Rmd
structure changed

Specificallt, by combining techno-typological information with stratigraphy and absolute chronology results, we present new data on: 1) the technological organization of levels 5/4E of Vale Boi, and levels U/T from Lapa do Picareiro; 2) a stratigraphical and chronological separation between Terminal Gravettian horizons and Proto-Solutrean occupations at both sites, revealing the application of the same general set of pattern to geographic areas outside of the Estremadura; 3) and, consequently, the validity of the two-stage model as the most likely.

# Archaeological sites

@@

After data collection, the databases, for both Vale Boi and Lapa do Picareiro, were imported into R environment, where the information was processed through the creation of descriptive statistical analysis. We include the entire R code used for all the analysis and visualizations contained in this paper is in our online research compendium at https://doi.org/. To produce those files, we followed the procedures described by Marwick et al. (XXXX) for the creation of research compendiums to enhance the reproducibility of research. To enable maximum re-use, our code is released under the MIT license, our data as CC-0, and our figures as CC-BY (for more information, see Marwick XXXX).

# Results

@@

## 4.1 Vale Boi

### 4.1.1 Assemblage and raw materials

@@

### 4.1.2 Technology

@@

## 4.2 Lapa do Picareiro

### 4.2.1 Assemblage and raw materials

@@

### 4.2.2 Technology

@@

# 5 Discussion

@@

# 6 Conclusion

>>>>

Specificallt, by combining techno-typological information with stratigraphy and absolute chronology results, we present new data on: 1) the technological organization of levels 5/4E of Vale Boi, and levels U/T from Lapa do Picareiro; 2) a stratigraphical and chronological separation between Terminal Gravettian horizons and Proto-Solutrean occupations at both sites, revealing the application of the same general set of pattern to geographic areas outside of the Estremadura; 3) and, consequently, the validity of the three-stage model as the best suited for the currently available data.

@@

After data collection, the databases were imported into R environment, where the information was processed through the creation of descriptive statistical analysis and writing of this article. We include the entire R code used for all the analysis and visualizations contained in this paper is in our online research compendium at https://doi.org/. To produce those files, we followed the procedures described by Marwick et al. (XXXX) for the creation of research compendiums to enhance the reproducibility of research. To enable maximum re-use, our code is released under the MIT license, our data as CC-0, and our figures as CC-BY (for more information, see Marwick XXXX).

@@

## Assemblage and raw materials

@@

### Technology

@@

## Assemblage and raw materials

@@

### Technology

@@

# Discussion

@@

# Conclusion
